<!--
%\VignetteEngine{knitr::docco_classic}
%\VignetteIndexEntry{bold vignette}
-->

`bold` is an R package to connect to BOLD Systems \url{http://www.boldsystems.org/} via their API. Functions in `bold` let you search for sequence data, specimen data, sequence + specimen data, and download raw trace files.

### bold info

+ [BOLD home page](http://boldsystems.org/)
+ [BOLD API docs](boldsystems.org/index.php/resources/api)

### Using bold

**Install**

Install `bold`

```{r, eval=FALSE}
devtools::install_github("ropensci/bold")
```

```{r}
library("bold")
```

### Search for sequence data only

Default is to get a list back

```{r}
bold_seq(taxon='Coelioxys')[1:2]
```

You can optionally get back the `httr` response object

```{r}
res <- bold_seq(taxon='Coelioxys', response=TRUE)
res$headers
```

### Search for specimen data only

By default you download `tsv` format data, which is given back to you as a `data.frame`

```{r}
res <- bold_specimens(taxon='Osmia')
head(res[,1:8])
```


### Search for specimen plus sequence data

By default you download `tsv` format data, which is given back to you as a `data.frame`

```{r}
res <- bold_seqspec(taxon='Osmia', sepfasta=TRUE)
res$fasta[1:2]
```

Or you can index to a specific sequence like

```{r}
res$fasta['GBAH0293-06']
```


### Get trace files

This function downloads files to your machine - it does not load them into your R session - but prints out where the files are for your information.

```{r cache=TRUE, cache.path="../ignore/"}
bold_trace(taxon='Osmia', quiet=TRUE)
```